US General Society Survey Analysis

### 2024-03-17 paper/paper.qmd
added the posterior checks and rhat stuff to appendix

```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences
  ),
  statistic = "mad"
  )
```

@@

@@

>>>>

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of presidential election in 2020 based on gender and immigration status"
#| warning: false
modelsummary(
  list(
    "Support Biden" = political_preferences
  ),
  statistic = "mad"
  )
```

@@

pp_check(political_preferences) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(political_preferences) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()

@@

plot(political_preferences, "trace")

plot(political_preferences, "rhat")
